\LARGE \bf Informed sampling by Markov Chain Monte Carlo methods

### 2017-01-24 paper.tex
enable hyperlink
add some mcmc

@@

MCMC~\cite{ADDJ03}

>>>>

\makeatletter
\let\NAT@parse\undefined
\makeatother

@@

Markov Chain Monte Carlo~\cite{ADDJ03} is a framework of sampling from a given probability distribution by constructing a Markov chain of random transition toward a desired distribution.
A set of samples are generated to approximate the desired distribution.
Unlike a rejection sampling, MCMC does a random walk in a parametric space and concentrates on an important areas, which usually brings better efficiency.
